\documentclass[a4paper,12pt]{article}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{fontspec}
\usepackage{natbib,bibentry}

% Font settings
\setmainfont{Times New Roman}

% Page layout settings
\geometry{top=0.75in, bottom=0.75in, left=0.75in, right=0.75in}

% Header and footer settings
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textbf{Curriculum Vitae}}
\fancyhead[R]{Aoxuan (Douglas) Li}
\fancyfoot[C]{\thepage}

% Title format
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}

\begin{document}

% Initialize bibliography linking to cv_bib.bib
\nobibliography{cv_bib.bib}
\bibliographystyle{alpha}

\begin{center}
    \textbf{\huge Aoxuan (Douglas) Li} \\
    \vspace{0.5em}
    \small \href{mailto:douglas.aox.li@gmail.com}{douglas.aox.li@gmail.com} | \textbf{Mobile:} (1) 747-228-2745 \\
\end{center}

\section*{Education}
\begin{itemize}[left=0pt, label={}]
    \item \textbf{PhD in Computer Science} \\
    IMDEA Software Institute, Dec 2024 -- Present
    \item \textbf{Master of Science in Computer Science} \\
    University of California, Los Angeles (UCLA), Sep 2017 -- Jun 2019 \\
    \emph{GPA: 3.81/4.0} | \textit{Master Thesis: On Explicit Depth Robust Graphs}
    \item \textbf{Bachelor of Science in Computing} \\
    Macao Polytechnic Institute, 2013 -- 2017 \\
    \emph{Overall GPA: 3.56/4.0}
\end{itemize}

\section*{Experience}
\begin{itemize}[left=0pt, label={}, itemsep=8pt]
    \item \textbf{Cryptographer | ExpandZK (Mystiko.Network)} \\
    Aug 2021 -- Dec 2024 (Freelance) | Nov 2020 -- Aug 2021
    \begin{itemize}[left=0pt,label=\textbullet,topsep=2pt]
        \item Designed the core protocol for \textbf{Mystiko.Network}, which achieved over \textbf{\$137M in total trading volume} and \$1M in protocol fees within its first year.
        \item Architected the decentralized auditing committee mechanism and optimized ZK-Rollup batching to reduce on-chain data costs by up to \textbf{90\%}.
    \end{itemize}

    \item \textbf{Researcher | Macao Polytechnic University, Macao \& University of Bologna, Italy} \\
    Aug 2021 -- Aug 2024
    \begin{itemize}[left=0pt,label=\textbullet,topsep=2pt]
        \item Conducted blockchain simulation research on ICP architecture advised by Prof. Gabriele D'Angelo.
        \item Researched distributed ledger technologies, DeFi confidentiality, and smart contract security.
    \end{itemize}

    \item \textbf{Cryptography Researcher (Intern) | Nethermind} \\
    Aug 2023 -- Nov 2023
    \begin{itemize}[left=0pt,label=\textbullet,topsep=2pt]
        \item Optimized STARK-based proof systems, reducing final argument proof size and verification complexity.
    \end{itemize}

    \item \textbf{Software Engineer | Stealth Software Technologies, Los Angeles} \\
    July 2019 -- July 2020
    \begin{itemize}[left=0pt,label=\textbullet,topsep=2pt]
        \item Contributed to \textbf{PULSAR/VLDS} (Verifiable Lean Database Systems) and \textbf{SAFRN} (Secure Architecture for Resilient Networks).
        \item Designed a novel Private Set Intersection (PSI) algorithm and implemented cryptographic primitives in Java.
    \end{itemize}

    \item \textbf{Graduate Research Assistant | UCLA (Cryptography Group)} \\
    Jan 2018 -- June 2019
    \begin{itemize}[left=0pt,label=\textbullet,topsep=2pt]
        \item Conducted theoretical cryptography research advised by \textbf{Prof. Rafail Ostrovsky}.
        \item Focused on the design of explicit depth-robust graphs and cryptographic protocol analysis.
    \end{itemize}

    \item \textbf{Graduate Research Assistant| UCLA (Cuneiform Digital Library Initiative)} \\
    Jan 2018 -- June 2019
    \begin{itemize}[left=0pt,label=\textbullet,topsep=2pt]
        \item Managed large-scale CentOS and MySQL server infrastructure for global digital heritage data.
        \item Optimized backup strategies for Docker-based virtualization and developed a CakePHP-based framework for data storage and display.
    \end{itemize}
\end{itemize}

\section*{Selected Publications}
\begin{itemize}[left=0pt, label={}, itemsep=2pt]
    \item \bibentry{li2025auditable}
    \item \bibentry{li2022modelling}
    \item \bibentry{li2023implementation}
    \item \bibentry{serena2022simulation}
    \item \bibentry{tang2023fully}
    \item \bibentry{li2019explicit}
\end{itemize}

\section*{Technical Skills \& Service}
\begin{itemize}[left=0pt, label={}]
    \item \textbf{Skills:} ZK-Proofs (STARKs), PSI, Blockchain Architecture, Python, Java, \LaTeX, SQL, Docker.
    \item \textbf{Academic Service:} Subreviewer for \textbf{Eurocrypt 2026/2019}, \textbf{CHES 2026}, and \textbf{INFOCOM 2023}.
    \item \textbf{Teaching:} TA for Security and Cryptography and Optimization Methods at MPU.
    \item \textbf{Languages:} Mandarin (Native), English (Fluent), Cantonese (Basic).
\end{itemize}

\end{document}